The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-01-29 paper/ms.tex
Added abstract.

\begin{abstract}
Abstract here
\end{abstract}

@@

@@

\section*{Acknowledgements}
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
It was supported by a start-up grant to Adam Kraus as well as a University of Texas Continuing Fellowship to Kevin Gullikson. J.-E. Lee was supported by the Basic Science Research Program through the National Research Foundation of Korea (NRF) (grant No. NRF-2015R1A2A2A01004769) and the Korea
Astronomy and Space Science Institute under the R\&D program (Project No. 2015-1-320-18) supervised by the Ministry of Science, ICT and Future Planning.

>>>>

\begin{abstract}
Binary stars and higher-order multiple systems are a ubiquitous outcome of star formation, especially as the system mass increases. The mass-ratio distribution is a unique probe into the physics of the collapsing molecular core as well as the circumstellar disk of the binary fragments. The mass-ratio distribution should change as the companion gets with $a \sim 1000$ AU, at which point the disks from the two forming stars can interact, and companions can form directly from the disk of the primary star. Unfortunately, close companions to A- and B-type stars are very difficult to detect and characterize because they are so much dimmer than the primary star. We present the results of a survey searching for companions to A- and B-type stars using the direct spectroscopic detection technique, which is sensitive to late-type companions within $\sim 1''$ of the primary. We estimate the temperatures and masses of the 58 companion detections, 25 of which are new detections. We present the mass-ratio distribution for our sample, and find that it is well described by a gaussian with mean of $q = 0.35 \pm 0.04$. TODO: discuss implications.
\end{abstract}
\keywords{binaries: spectroscopic, stars:early-type, stars:formation, stars:statistics}

@@

TODO: Discuss the stars I actually use in the fit, and the ones I don't!

@@

\section*{Acknowledgements}
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
It was supported by a start-up grant to Adam Kraus as well as a University of Texas Continuing Fellowship to Kevin Gullikson.
